---
title:  "VAT Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: css/styles-default.css
    logo: img/WB_pic.ico
---

<style type="text/css">
.value-box .value {
    color: white;
}
.value-box .caption {
    color: white;
}
</style>

```{r setup, include=FALSE}

# Setting icons
# https://www.angularjswiki.com/fontawesome/logistics/
 

```

# Intro

This dashboard include several types of results:

-	Decomposition of VAT GAP
-	Policy Simulation
-	Structure of non-refundable VAT by sectors
-	Estimation of tax expenditures
-	Estimation of effective VAT rates
-	Distributional impacts of a policy on households by COICOP


Definitions for VAT-GAP:

- Total VAT Gap: difference between the VAT control total and benchmark VAT;
- Policy Gap: additional revenue that would be gained if the tax relief granted through
policy decisions was eliminated; and
- Compliance Gap: Total VAT gap less the component attributable to policy decisions.


Exec Summary
=======================================================================


Column {data-width=250}
-----------------------------------------------------------------------
### **KPIs**
### VAT Benchmark Rate

```{r}

valueBox(VAT_Benchmark_Rate,
         icon="fa-percent",
          color = "orange")


```



### Benchmark VAT (in LCU millions)

```{r}

valueBox(Benchmark_VAT,
         icon="fa-coins",
          color = "#17becf")

```

### Uncalibrated VAT (in LCU millions)

```{r}

valueBox(Uncalibrated_VAT,
          icon="fa-balance-scale-left",
          color = "green")


```

### Calibrated VAT (in LCU millions)

```{r}

valueBox(Calibrated_VAT,
         icon="fa-balance-scale",
          color = "red")

```


### Total VAT_Gap (in LCU millions)

```{r}

valueBox(Total_VAT_Gap,
         icon="fa-money-check-alt",
         color = '#103d5d')


```

### Policy Gap (in LCU millions)

```{r}

valueBox(Policy_Gap,
         icon="fa-hand-holding-usd",
          color = '#e377c2'
          )


```


### Compliance Gap (in LCU millions)

```{r}

valueBox(Compliance_Gap,
         icon="fa-chart-area",
          color = "#bcbd22")


```




Column {data-width=350}
-----------------------------------------------------------------------
### **Gauge charts**
### VAT GAP (%)

```{r}
  gauge_vat_gap_pct<-gauge(Total_VAT_Gap_Pct$Actual,min=0,max=100,
           gaugeSectors(danger = c(71,100),
                        warning = c(31,70),
                        success = c(0,30)))

gauge_vat_gap_pct

```

### Policy Gap (%)

```{r}

  gauge_vat_policy_pct<-gauge(Policy_Gap_Pct$Actual,min=0,max=100,
           gaugeSectors(danger = c(71,100),
                        warning = c(31,70),
                        success = c(0,30)))
                      
gauge_vat_policy_pct

```


### Compliance Gap (%)

```{r}

  gauge_vat_policy_compliance_pct<-gauge(Compliance_Gap_Pct$Actual,min=0,max=100,
           gaugeSectors(danger = c(71,100),
                        warning = c(31,70),
                        success = c(0,30)))
                      
gauge_vat_policy_compliance_pct

```


### C-Efficency

```{r}

  gauge_vat_policy_compliance_pct<-gauge(C_Efficiency$Actual,min=0,max=1,
           gaugeSectors(success = c(0.70,1),
                        warning = c(0.31,0.69),
                        danger = c(0,0.3)))
                      
gauge_vat_policy_compliance_pct

```


### VAT GAP as share of GDP

```{r}

  gauge_vat_share_pct_gdp<-gauge(round((Total_VAT_Gap/GDP_2022)*100,2)[1,1],min=0,max=100,
           gaugeSectors(danger = c(71,100),
                        warning = c(31,70),
                        success = c(0,30)))
gauge_vat_share_pct_gdp

```



Column {data-width=650}
-----------------------------------------------------------------------

### **Tax Expenditures**

```{r}
BarChart_TE

```


Historic
=======================================================================

Row
-----------------------------------------------------------------------

### 

```{r}


VAT_PctOfGDP

```

### 

```{r}
    
                           
VAT_Revenues_Nominal

```

Row
-----------------------------------------------------------------------

### 

```{r,eval=TRUE}

 
                            
                            StructureOfTaxRevenues_Nominal

```


### 

```{r,eval=TRUE}


                            
                            VAT_StructureOfTaxRevenuesPct



                       
```


VAT Structure
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### VAT revenues from Industries (in LCU millions)
```{r,eval=TRUE}

valueBox(round(sum(VAT_Industries$Total_Revenues_from_Intermediate_Inputs)/1000,0),
         icon="fa-industry",
          color = "blue")
```


### VAT revenues from industries 

```{r,eval=TRUE}

              
VAT_revenues_industries_treemap

``` 

Row
-----------------------------------------------------------------------

### VAT revenues from NPISH (in LCU millions)
```{r,eval=TRUE}


valueBox(round(sum(VAT_NPISH$Final_Demand_NPISH)/1000,0),
         icon="fa-chart-pie",
          color = "red"
         )
```


### VAT revenues from NPISH 
```{r,eval=TRUE}

VAT_revenues_NPISH_treemap

``` 

Row
-----------------------------------------------------------------------
### VAT revenues from Government (in LCU millions)
```{r,eval=TRUE}

valueBox(round(sum(VAT_Government$Final_Demand_Government)/1000,0),
         icon="fa-landmark",
          color = "orange")
```


### VAT revenues from Government 

```{r,eval=TRUE}

    VAT_revenues_Government_treemap

``` 

Row
-----------------------------------------------------------------------

### VAT revenues from households (in LCU millions)
```{r,eval=TRUE}




valueBox(round(sum(VAT_Households$Final_Demand_HH)/1000,0),
         icon="fa-home",
          color = "green")
```


### VAT revenues from households 
```{r,eval=TRUE}

    
    VAT_revenues_Households_treemap
``` 


Tax Expenditures
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Total tax expenditures (in LCU millions)
```{r,eval=TRUE}

valueBox(round(te_agg_value_box,0),
         icon="fa-chart-line",
          color = "blue")
```


### 

```{r,eval=TRUE}


Plot_Standard_Actual_Rates

```

Row
-----------------------------------------------------------------------

### Percentage change in VAT revenues
```{r,eval=TRUE}

valueBox(round(te_agg_value_pct,1),
         icon="fa-chart-pie",
          color = "red")

```


### 

```{r,eval=TRUE}


BarChart_TE



```


Simulation Results
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Fiscal impact of simulation (in LCU millions)
```{r,eval=TRUE}

valueBox(round(filtered_results_value_box,0),
         icon="fa-cash-register",
          color = "blue")
```


### 

```{r,eval=TRUE}
 



BarChart_Simulation


```








